\chapter{Towards Model-based Run-time State Migration}
In this chapter we discuss requirements and a potential solution towards an approach for supporting run-time state migration. Moreover, we analyze some same-purpose applications to identify requirements for our DSL and to know which migratable run-time states are involved in the application's scope..

\label{ch:requirements}

\section{Requirements Analysis}
This section provides a requirements for a run-time state migration approaches for same-purpose application of different vendors. The rationale behind every requirement is given when discussing the individual requirements. 

\subsection{R1 Applicable on Existing Applications}
This approach shall allow enabling run-time state migration on new and existing same-purpose applications. The source code of these applications must be accessible. Developers should be able to use this approach on applications, even if they are not part of the applications' developers team. Thereby, it enables the support of a vast number of existing applications.


\subsection{R2 Platform-independent State Specification}
It shall be possible to model which and when parts of existing applications can be migrated. Also, as the approach meant to work of different platforms, it shall be possible to model these states in a platform-independent manner.

\subsection{R3 Model Repository}
Developers wanting to adapt the run-time state migration approach to existing application, shall write a state specification or have access to existing state specification. Thereby, it shall be possible to have a central place to store models that are state specifications. Developers can search for common models or upload models they defined. This repository helps wider possibilities for migration, more reuse and reduce the time of development. 

\subsection{R4 Device Management}
It must be possible to find, list and select devices offering the same states and migrate them. Also, the device discovery shall be possible in a way that the approach can express if a device knows another devices has the same run-time state on the same network.


\section{Same-purpose Applications Analysis}
\input{chapters/4-requirements/applications}

\section{Requirements for a DSL}
\input{chapters/4-requirements/dsl}

\section{Solution Overview}
\input{chapters/4-requirements/solution}